\documentclass[12pt]{article} % text width
\usepackage[utf8]{inputenc} % encode text to utf8

\usepackage[english]{babel} % text correction
\usepackage[a4paper]{geometry}

% quotes and bibliography
\usepackage{dirtytalk}
\usepackage{csquotes}
\usepackage[
backend=biber,
style=numeric,
sorting=ynt
]{biblatex}
\addbibresource{biblio.bib} % bibliography

\title{Comparison of consensus algorithms for blockchain applications}
\author{Florian Rascoussier}
\date{March 2022}

\pagenumbering{roman} % set page numbering of front matter sections

% use acronyms and glossaries
% toc: add glossary to table of contents
\usepackage[colorlinks]{hyperref}
\usepackage[acronym, toc]{glossaries} 
\input{glossaries.tex} % acronyms definitions

% document content
\begin{document}

\input{title.tex}
\newpage

\input{cover.tex}
\newpage

\section{Abstract}
In this report, we will try to do a comparison between different consensus 
algorithms for blockchain applications. Overviews of those algorithms 
already exist in the literature. However, we will both try to present
new or not well known algorithms as well as try to measure the 
differences by conducting experiments with code.

\section{Acknowledgement}
Special thanks to the supervisors of this PhD Track project, namely:
\begin{itemize}
    \item Lionel Brunie
    \item Omar Hasan
\end{itemize}

\section{Foreword}
This report will be using abbreviations and acronyms, especially for the following:
\begin{itemize}
    \item consensus algorithms
    \item consensus protocols
    \item other algorithms
\end{itemize}
When possible, they will be defined in the text between parenthesis right after 
the first occurrence of the word or expression. Each of these abbreviations will 
be available in the 

\newpage
\tableofcontents

\newpage
\pagenumbering{arabic} % reset page numbering

\section{Introduction}
Since the introduction of the Bitcoin protocol and its 
\say{\acrlong{PoW}} \cite{Nakamoto2009-uw}, consensus algorithms have 
seen a rapid development and diversification. 

Another now well-known consensus algorithm is the \acrlong{PoS}, which
was first introduced in...

\subsection{Context of the report}
This report has been written in the context of a Phd-Track project. This
is a Double-Degree program between INSA Lyon and Universität Passau. This 
Double-Degree is heavily research oriented. It is intended to prepare 
students to research and is a first step towards a PhD-Degree.

\subsection{Consensus Algorithms}

\subsection{Blockchain types and impact}

\section{}


\section{Conclusion}

\newpage
\section{Appendices}

% glossary and acronyms
\printglossary[type=\acronymtype]
\printglossary


\newpage
\input{biblio.tex}

\subsection{Bibliography} % to be removed


\restoregeometry
\end{document}